\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Norman Alaskari}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{normanalaskari.wixsite.com/website}
% vs how you want it to show up. If it's you can just replace "\yourWebsiteLink" with "yourWebsite"
\newcommand{\yourEmail}{norman.alaskari@gmail.com}
\newcommand{\yourPhone}{1-210-812-9431}
\newcommand{\githubUserName}{normAlaskari}
\newcommand{\linkedInUserName}{n-alaskari}

% An alternate profile section 
% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsiteLink}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsiteLink}{\yourWebsite}
%     \\
% \end{tabular*}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    % $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
\end{center}

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{ASSET WORKS LLC}{Software Quality Assurance Analyst}{San Antonio, TX}{Feb 2020 – May 2021}
\begin{bullets}
    \item Tested Products, generated network diagrams, created and ran scripts in \textbf{SQL}, \textbf{Java}, and \textbf{JMX}.
    %  \item Here is another bullet that I might choose to uncomment for some jobs   \under
    \item Wrote and executed test cases using \textbf{JIRA} and other tools.
    \item Learned \textbf{JMeter},an open source functional load testing tool 
    \item Developed and execute functional performance tests against several applications
    \item Configured and Document the environment in which the tests are run
    \item Documented the steps required to execute the tests
    \item Documented the results of the tests and review with Product Manager.
\end{bullets}
\sectionsep

\resumeHeading{H-E-B Grocery Company}{Full-stack Developer Intern}{San Antonio, TX}{Jul 2020 - May 2021}
\begin{bullets} 
    \item Designed client-side and server-side architecture.
    \item Developed and manage well-functioning databases and applications Write effective APIs. 
    \underlinedLink{http://volunteer-tracker.dev.university2heb.com/}{volunteer-tracker}.
    \item Created private cloud using \textbf{Kubernetes} that supports DEV, TEST, and PROD environments.
    \item Built and deployed \textbf{CI/CD} pipelines.
    \item Created a Continuous Delivery process to include support building of  \textbf{Docker} Images and publish into a private repositor.
    \item Used \textbf{CI/CD} tools \textbf{Jenkins},\textbf{Git/Gitlabs}, \textbf{Jira} and \textbf{Docker} registry/daemon for configuration management and automation using \textbf{Ansible}.
    \item Experience in providing highly available and fault tolerant applications utilizing orchestration technologies like \textbf{Kubernetes} and Apache Mesos on \textbf{Google Cloud Platform}.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Strixhaven Rowdyhack}{https://github.com/jacksonSingleton/RowdyHacks2021}{JavaScript, React, TypeScript, HTML, CSS, Docker}
The User opens the site and is introduced to a tutorial and tests out specific spells prompted in the middle of the screen.
The User is then brought into a sandbox area to play around with the provided spells.
\sectionsep
  
\projectHeading{
SpaceBrawl}{https://github.com/BioCyan/SpaceBrawl}{Java, JavaFX}
SpaceBrawl is a simple space shooter game where the players shoots asteroids to gain points while orbiting a star. It uses JavaFX for both its menus and 3D features.\\
\sectionsep

\projectHeading{Colorizing The Past Project}{https://github.com/normAlaskari/Colorize_The_past}{Python, google.colab, CNN, Big Data}
Our group decided to use a Convolutional Neural Network (CNN) in order to color
images. Our primary goal is to add color to old photos, photos that were taken before the invention of colored film.
\sectionsep

% Example using bullets and dates 
% \projectHeadingWithDate{Hogwart\textquotesingle{}s Library Management System}{https://github.com/Aarif123456/hogwartslibrary}{PHP, JavaScript, HTML, CSS, MySQL}{Aug 2019}
% \begin{bullets}
    % \item A full-stack library management system, where users can manage books and holds on their accounts. Users can search the library\textquotesingle{}s catalogue, which has every book mentioned in the Harry Potter series. The system distinguishes between 4 users. For examples, librarians who can also check or return books on behalf of users.\\
% \end{bullets}
% \sectionsep
  

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{skillList}
    \singleItem{Languages:}{Java, C++, Python, C\#, PHP, Bash, C, Dart (Flutter),Lisp , Flaks}
    \\
    \singleItem{Web Development:}{React, JavaScript, TypeScript, HTML/CSS}
    \\
    \singleItem{Technology:}{Git, AWS, GCP, Azure, Docker, Unity, Apache, LaTex} \\
    {Jenkins, Kubernetes, Uinx , Vi/VIM , LaTex , Sed/Awk , Jmeter, Apache Tomcat, Selenium}
    \\
    \singleItem{Databases:}{SQL,NoSQL,Graph SQL, MongoDB, Postgres, DynamoDB}
\end{skillList}

% A more concise alternate 
% \begin{skillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Bash, C, SQL , NoSQL, Dart (Flutter),Lisp , Flaks}%
%     {Databases:}{Databases:}{SQL,NoSQL,Graph SQL, MongoDB, Postgres, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{skillList}



%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Put school first and degree second if your school is reputable
\educationHeading{BSc. Honours Computer Science With Software Engineering and Data science Specialization}{The University Of Texas At San Antonio}{San Antonio, TX}{May 2021}
\\
\educationHeading{ASc. Honours Computer Science }{Del Mar Collage}{corpus christi, TX}{December 2019}
\sectionsep
\end{document}
